Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-18 paper/paper.qmd
update paper.qmd and references.bib
script to convert rds to txt

>>>>

```{r}
library(knitr)

# Load the model from the RDS file
loaded_model <- readRDS(here::here("models/linear_model.rds"))

# Capture the console output
output <- capture.output(summary(loaded_model))

# Write the captured output to a text file
writeLines(output, "model_summary.txt")

# Render the text file as a picture
system(paste("convert -density 300 model_summary.txt model_summary.png"))

# Display the saved image
include_graphics("model_summary.png")
